---
title: "002_Trim_Metabolism"
author: "Bella Oleksy"
date: "3/23/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir='..')
knitr::opts_chunk$set(out.width = '50%',fig.height=10) 
# knitr::opts_chunk$set(
#  fig.width = 6,
#  fig.asp = 0.8,
#  out.width = "80%"
# )
library(here)
source(here("r_code/librariesAndFunctions.R"))


```


## Trimming metabolism

Here, I am experimenting with trimming down the GPP results and seeing how it changes the mean/median estimates for each lake 


```{r load raw metab, include=FALSE}

# Pull in metab data
source(here("r_code/dataPullMetab.R"))

rm(cur)
rm(dontuse)
rm(MueggelseeZMix)

#Read in metadata google sheet
metadata<-read_sheet("https://docs.google.com/spreadsheets/d/1is87WT3n_TU76pTyiis3Os08JJiSmWc2G6K4bthJhU8/edit#gid=952562522") 

#and join

bella_metab_withMetaData <- left_join(bella_metab, metadata, by = c('lakeName'))



```


```{r echo=FALSE}
##SUMMER ONLY
# Trim to only "summer" dates. In the northern hemisphere this is June1-Sept1, and in the southern hemisphere this is Dec1-April1. 
bella_metab_withMetaData<- bella_metab_withMetaData %>%
  select(solarDay, lakeName, GPP_mgCm2, `Latitude (decimal degrees)`) %>%
  mutate(year=year(solarDay),
         DOY=yday(solarDay), 
         hemisphere = ifelse(`Latitude (decimal degrees)` < 0, #Assign northern or southern hemisphere
                        "southern", 
                        "northern")) %>% 
  mutate(summer_start = ifelse(hemisphere=="northern",
                        152, #June 1 - summer start n. hemisphere
                        335), #Dec 1 -  summer start s. hemisphere
         summer_end = ifelse(hemisphere=="northern",
                        244, #Sept 1 - summer end n. hemisphere
                        91)) #April 1- summer end s. hemisphere

#Divide into two dataframes by hemisphere, otherwise couldn't get case_when() to work 
bella_metab_withMetaData_northern<- bella_metab_withMetaData %>%
  filter(hemisphere=="northern")%>%
  mutate(season = case_when(hemisphere=="northern" & DOY > summer_start & DOY < summer_end ~ "summer",  # specify when the "summer" season 
                            hemisphere=="northern" & DOY >= 121 & DOY <= 152 | DOY >= 244 & DOY < 274 ~ "+", # specify when the "+" season
                            T ~ "other"))  # all others = "other"
  
bella_metab_withMetaData_southern<- bella_metab_withMetaData %>%
  filter(hemisphere=="southern")%>%
  mutate(season = case_when(hemisphere=="southern" & DOY > summer_start | DOY < summer_end ~ "summer",# specify when the "summer" season 
                            hemisphere=="southern" & DOY >= 91 & DOY <= 121 | DOY >= 305 & DOY < 335 ~ "+", # specify when the "+" season
                            T ~ "other"))  

bella_metab_withMetaData <- bind_rows(bella_metab_withMetaData_northern,bella_metab_withMetaData_southern)

bella_metab_summer<-bella_metab_withMetaData %>%
  filter(season=="summer")

##EXTENDED SUMMER -- add a month on either end
# Trim to only "summer" dates. In the northern hemisphere this is June1-Sept1, and in the southern hemisphere this is Dec1-April1. 
bella_metab_withMetaData_extendedSummer<- bella_metab_withMetaData %>%
  select(solarDay, lakeName, GPP_mgCm2, `Latitude (decimal degrees)`) %>%
  mutate(year=year(solarDay),
         DOY=yday(solarDay), 
         hemisphere = ifelse(`Latitude (decimal degrees)` < 0, #Assign northern or southern hemisphere
                        "southern", 
                        "northern")) %>% 
  mutate(summer_start = ifelse(hemisphere=="northern",
                        121, #May 1 - summer start n. hemisphere
                        305), #Nov 1 -  summer start s. hemisphere
         summer_end = ifelse(hemisphere=="northern",
                        274, #Oct 1 - summer end n. hemisphere
                        121)) #May 1- summer end s. hemisphere

#Divide into two dataframes by hemisphere, otherwise couldn't get case_when() to work 
bella_metab_withMetaData_northern_extendedSummer<- bella_metab_withMetaData_extendedSummer %>%
  filter(hemisphere=="northern")%>%
  mutate(season = case_when(hemisphere=="northern" & DOY > summer_start & DOY < summer_end ~ "summer",
                            T ~ "other"))  # specify when the "summer" season is in effect in either hemisphere
bella_metab_withMetaData_southern_extendedSummer<- bella_metab_withMetaData_extendedSummer %>%
  filter(hemisphere=="southern")%>%
  mutate(season = case_when(hemisphere=="southern" & DOY > summer_start | DOY < summer_end ~ "summer",
                            T ~ "other"))  # specify when the "summer" season is in effect in either hemisphere

bella_metab_withMetaData_extendedSummer <- bind_rows(bella_metab_withMetaData_northern_extendedSummer,
                                                     bella_metab_withMetaData_southern_extendedSummer)

bella_metab_extendSummer<-bella_metab_withMetaData_extendedSummer %>%
  filter(season=="summer")

#Summarie the raw dataframe
bella_metab_summary <- bella_metab %>%
  group_by(lakeName) %>% 
  summarise(n=n(),
            n_NAs=sum(is.na(GPP_mgCm2)),
            mean= mean(GPP_mgCm2, na.rm = T) , 
            median = median(GPP_mgCm2, na.rm= T),
            sdGPP= sd(GPP_mgCm2, na.rm = T)) %>% 
  mutate(seGPP=sdGPP/sqrt(n),
         GPP5=mean+qnorm(0.05)*seGPP,
         GPP25=mean+qnorm(0.25)*seGPP,
         GPP50=mean+qnorm(0.5)*seGPP,
         GPP75=mean+qnorm(0.75)*seGPP,
         GPP95=mean+qnorm(0.95)*seGPP,
         dataset="raw") 

bella_metab_summary_long<-bella_metab_summary %>%
    pivot_longer(-c(lakeName, dataset), names_to="variable",
               values_to="value")


#Summarize the "summer only" dataframe
bella_metab_summer_summary <- bella_metab_summer %>%
  group_by(lakeName) %>% 
  summarise(n=n(),
            n_NAs=sum(is.na(GPP_mgCm2)),
            mean= mean(GPP_mgCm2, na.rm = T) , 
            median = median(GPP_mgCm2, na.rm= T),
            sdGPP= sd(GPP_mgCm2, na.rm = T)) %>% 
  mutate(seGPP=sdGPP/sqrt(n),
         GPP5=mean+qnorm(0.05)*seGPP,
         GPP25=mean+qnorm(0.25)*seGPP,
         GPP50=mean+qnorm(0.5)*seGPP,
         GPP75=mean+qnorm(0.75)*seGPP,
         GPP95=mean+qnorm(0.95)*seGPP,
         dataset="summer") 

bella_metab_summer_summary_long<- bella_metab_summer_summary %>%
    pivot_longer(-c(lakeName, dataset), names_to="variable",
               values_to="value")

#Summarize the "extended summer" dataframe

bella_metab_extendSummer_summary <- bella_metab_extendSummer %>%
  group_by(lakeName) %>% 
  summarise(n=n(),
            n_NAs=sum(is.na(GPP_mgCm2)),
            mean= mean(GPP_mgCm2, na.rm = T) , 
            median = median(GPP_mgCm2, na.rm= T),
            sdGPP= sd(GPP_mgCm2, na.rm = T)) %>% 
  mutate(seGPP=sdGPP/sqrt(n),
         GPP5=mean+qnorm(0.05)*seGPP,
         GPP25=mean+qnorm(0.25)*seGPP,
         GPP50=mean+qnorm(0.5)*seGPP,
         GPP75=mean+qnorm(0.75)*seGPP,
         GPP95=mean+qnorm(0.95)*seGPP,
         dataset="summer+") 

bella_metab_extendSummer_summary_long<- bella_metab_extendSummer_summary %>%
    pivot_longer(-c(lakeName, dataset), names_to="variable",
               values_to="value")

#Create first comparison dataframe
comparison1<-bind_rows(bella_metab_summary, bella_metab_summer_summary)
comparison2<-bind_rows(bella_metab_summary, bella_metab_summer_summary,bella_metab_extendSummer_summary)
comparison1_long<-bind_rows(bella_metab_summary_long, bella_metab_summer_summary_long)
comparison2_long<-bind_rows(bella_metab_summary_long, bella_metab_summer_summary_long,bella_metab_extendSummer_summary_long)
```


### Boxplots - summer only versus un-trimmed
Most, but not all, lakes end up having higher GPP overall if we trim to summer. Note that Prairie Lake drops out because there are only about 2 weeks of data for this lake, and it doesn't fall in the "summer" window.
```{r, out.width = '100%',fig.height=15}

# comparison1 %>%
#   ggplot(aes(x=dataset, y=mean, fill=dataset))+
#   geom_boxplot(aes(ymin = GPP5,
#                    lower = GPP25,
#                    middle = GPP50,
#                    upper = GPP75,
#                    ymax = GPP95),
#                stat='identity')+
#   ggtitle("Boxplot comparisons")+
#   ylab(expression(paste('GPP (mg O2 m'^-2,' day'^-1,')')))+
#   theme_bw()+
#     scale_fill_manual(values=c("red","blue"))+
#   facet_wrap(.~lakeName, scales="free", ncol=5)+
#   theme(legend.position="none",
#         axis.title.x=element_blank())


comparison2 %>%
  ggplot(aes(x=dataset, y=mean, fill=dataset))+
  geom_boxplot(aes(ymin = GPP5,
                   lower = GPP25,
                   middle = GPP50,
                   upper = GPP75,
                   ymax = GPP95),
               stat='identity')+
  ggtitle("Boxplot comparisons")+
  ylab(expression(paste('GPP (mg C m'^-2,' day'^-1,')')))+
  theme_bw()+
  scale_fill_manual(values=c("red","blue","green"))+
  facet_wrap(.~lakeName, scales="free", ncol=5)+
  theme(legend.position="none",
        axis.title.x=element_blank())
```


<!-- ### Looking just at median and mean values -->
<!-- Most of the time, the median is quite a bit lower than the mean. This is the case in the "raw" and "trimmed" dataset -->
<!-- ```{r, out.width = '100%',fig.height=15} -->
<!-- #  -->
<!-- # comparison1_long %>%  -->
<!-- #   filter(variable %in% c("mean","median"))%>% -->
<!-- #   ggplot(aes(x=variable, y=value, fill=dataset, shape=variable))+ -->
<!-- #   geom_point(size=3)+ -->
<!-- #   scale_shape_manual(values=c(21,25), -->
<!-- #                      name="Variable")+ -->
<!-- #   scale_fill_manual(values=c("red","blue"))+ -->
<!-- #   ylab(expression(paste('GPP (mg O2 m'^-2,' day'^-1,')')))+ -->
<!-- #   ggtitle("Mean and median comparisons")+ -->
<!-- #   theme_bw()+ -->
<!-- #   facet_wrap(.~lakeName, scales="free", ncol=5)+ -->
<!-- #   guides(fill = guide_legend(override.aes=list(shape=21)))+ -->
<!-- #   theme(axis.title.x=element_blank(), -->
<!-- #         legend.position="top") -->

<!-- comparison2_long %>%  -->
<!--   filter(variable %in% c("mean","median"))%>% -->
<!--   ggplot(aes(x=variable, y=value, fill=dataset, shape=variable))+ -->
<!--   geom_point(size=3)+ -->
<!--   scale_shape_manual(values=c(21,25), -->
<!--                      name="Variable")+ -->
<!--   scale_fill_manual(values=c("red","blue","green"))+ -->
<!--   ylab(expression(paste('GPP (mg O2 m'^-2,' day'^-1,')')))+ -->
<!--   ggtitle("Mean and median comparisons")+ -->
<!--   theme_bw()+ -->
<!--   facet_wrap(.~lakeName, scales="free", ncol=5)+ -->
<!--   guides(fill = guide_legend(override.aes=list(shape=21)))+ -->
<!--   theme(axis.title.x=element_blank(), -->
<!--         legend.position="top") -->

<!-- ``` -->

# Comparison across lakes
How does this change the distribution of GPP across lakes? 

```{r echo=FALSE, fig.height=4, out.width='100%'}
bella_metab_summary %>% 
  rename(meanGPP=mean)%>%
  ggplot(aes(x=reorder(lakeName, meanGPP, FUN=mean), y=meanGPP))+
  geom_boxplot(aes(ymin = GPP5,
                   lower = GPP25,
                   middle = GPP50,
                   upper = GPP75,
                   ymax = GPP95),
               fill="red",
               stat='identity')+
  ylab(expression(paste('GPP (mg O2 m'^-2,' day'^-1,')')))+
  ggtitle("Original data - not trimmed")+
    theme_bw()+
  theme(legend.position="none",
        axis.title.x=element_blank(),
        axis.text.x=element_text(angle = 45, hjust = 1, size=6))+
    scale_y_log10()
  
bella_metab_summer_summary %>% 
    rename(meanGPP=mean)%>%
  ggplot(aes(x=reorder(lakeName, meanGPP, FUN=mean), y=meanGPP))+
  geom_boxplot(aes(ymin = GPP5,
                   lower = GPP25,
                   middle = GPP50,
                   upper = GPP75,
                   ymax = GPP95),
               fill="blue",
               stat='identity')+
  ylab(expression(paste('GPP (mg O2 m'^-2,' day'^-1,')')))+
  ggtitle("Daily values trimmed to summer")+
    theme_bw()+
  theme(legend.position="none",
        axis.title.x=element_blank(),
        axis.text.x=element_text(angle = 45, hjust = 1, size=6))+
    scale_y_log10()

bella_metab_extendSummer_summary %>% 
    rename(meanGPP=mean)%>%
  ggplot(aes(x=reorder(lakeName, meanGPP, FUN=mean), y=meanGPP))+
  geom_boxplot(aes(ymin = GPP5,
                   lower = GPP25,
                   middle = GPP50,
                   upper = GPP75,
                   ymax = GPP95),
               fill="green",
               stat='identity')+
  ylab(expression(paste('GPP (mg O2 m'^-2,' day'^-1,')')))+
  ggtitle("Daily values trimmed to summer + a month of either end")+
    theme_bw()+
  theme(legend.position="none",
        axis.title.x=element_blank(),
        axis.text.x=element_text(angle = 45, hjust = 1, size=6))+
    scale_y_log10()



```

It shuffles things around a little bit, but overall our top 5 most/least productive lakes are the same lakes. 

Top 5 least productive (untrimmed): `r bella_metab_summary %>% arrange(GPP50) %>% select(lakeName) %>% slice_head(n=5)`
Top 5 least productive (summer only): `r bella_metab_summer_summary %>% arrange(GPP50) %>% select(lakeName) %>% slice_head(n=5)`
Top 5 least productive (extended summer): `r bella_metab_extendSummer_summary %>% arrange(GPP50) %>% select(lakeName) %>% slice_head(n=5)`


Top 5 most productive (untrimmed): `r bella_metab_summary %>% arrange(desc(GPP50)) %>% select(lakeName) %>%  slice_head(n=5)`
Top 5 most productive (summer only): `r bella_metab_summer_summary %>% arrange(desc(GPP50)) %>% select(lakeName) %>%  slice_head(n=5)`
Top 5 most productive (extended summer): `r bella_metab_extendSummer_summary %>% arrange(desc(GPP50)) %>% select(lakeName) %>%  slice_head(n=5)`


### Examine a few lakes more closely
I wanted to start by looking at the a few lakes where GPP was lower after trimming

<b>Balaton.</b> In this case, estimated GPP in the trimmed dataset is about <i>half</i> of the full dataset because we end up missing some high GPP days in late August/early September. 
```{r, out.width = '100%',fig.height=5}

boxplot<-comparison2 %>%
  filter(lakeName=="Balaton")%>%
  ggplot(aes(x=dataset, y=mean, fill=dataset))+
  geom_boxplot(aes(ymin = GPP5,
                   lower = GPP25,
                   middle = GPP50,
                   upper = GPP75,
                   ymax = GPP95),
               stat='identity')+
  ggtitle("Lake Balaton")+
  ylab(expression(paste('GPP (mg O2 m'^-2,' day'^-1,')')))+
  theme_bw()+
    scale_fill_manual(values=c("red","blue","green"))+
  theme(legend.position="none",
        axis.title.x=element_blank())

timeseries<-bella_metab_withMetaData %>%
  filter(lakeName=="Balaton")%>%
  ggplot(aes(x=solarDay,y=GPP_mgm2, fill=season))+
  geom_point(size=3, shape=21)+
  scale_fill_manual(values=c("lightgreen","white","forestgreen"))+
    ylab(expression(paste('GPP (mg O2 m'^-2,' day'^-1,')')))+
  theme_bw()

boxplot+timeseries +
  plot_layout(widths = c(1, 2))
```


<b>TheLoch.</b> In this case, estimated GPP in the trimmed dataset is about <i>half</i> of the full dataset because we end up missing some high GPP days in late August/early September. 
```{r, out.width = '100%',fig.height=5}

boxplot<-comparison2 %>%
  filter(lakeName=="TheLoch")%>%
  ggplot(aes(x=dataset, y=mean, fill=dataset))+
  geom_boxplot(aes(ymin = GPP5,
                   lower = GPP25,
                   middle = GPP50,
                   upper = GPP75,
                   ymax = GPP95),
               stat='identity')+
  ggtitle("The Loch")+
  ylab(expression(paste('GPP (mg O2 m'^-2,' day'^-1,')')))+
  theme_bw()+
    scale_fill_manual(values=c("red","blue","green"))+
  theme(legend.position="none",
        axis.title.x=element_blank())

timeseries<-bella_metab_withMetaData %>%
  filter(lakeName=="TheLoch")%>%
  ggplot(aes(x=solarDay,y=GPP_mgm2, fill=season))+
  geom_point(size=3, shape=21)+
  scale_fill_manual(values=c("lightgreen","white","forestgreen"))+
    ylab(expression(paste('GPP (mg O2 m'^-2,' day'^-1,')')))+
  theme_bw()

boxplot+timeseries +
  plot_layout(widths = c(1, 2))
```
Knowing this lake pretty well (one of my dissertation lakes), I'm surprised to see a late season peak. Given that these rates are still quite low, I'm comfortable trimming the data to < Sept 1.


<b>Trout Lake.</b> Overall this is a super unproductive lake, but with the Sept 1 cut-off we do see to miss part of a second "peak" in September. 
```{r, out.width = '100%',fig.height=5}

boxplot<-comparison2 %>%
  filter(lakeName=="Trout")%>%
  ggplot(aes(x=dataset, y=mean, fill=dataset))+
  geom_boxplot(aes(ymin = GPP5,
                   lower = GPP25,
                   middle = GPP50,
                   upper = GPP75,
                   ymax = GPP95),
               stat='identity')+
  ggtitle("Trout Lake")+
  ylab(expression(paste('GPP (mg O2 m'^-2,' day'^-1,')')))+
  theme_bw()+
    scale_fill_manual(values=c("red","blue","green"))+
  theme(legend.position="none",
        axis.title.x=element_blank())

timeseries<-bella_metab_withMetaData %>%
  filter(lakeName=="Trout")%>%
  filter(GPP_mgm2<1)%>%
  ggplot(aes(x=solarDay,y=GPP_mgm2, fill=season))+
  geom_point(size=3, shape=21)+
  scale_fill_manual(values=c("lightgreen","white","forestgreen"))+
    ylab(expression(paste('GPP (mg O2 m'^-2,' day'^-1,')')))+
  theme_bw()

boxplot+timeseries +
  plot_layout(widths = c(1, 2))
```



<b>Little Rock Lake.</b>  This is a NEON lake, where they used DO profilers rather than stationary DO sensors (among other continuity issues with their wind, temp sensors), so I ended up with a pretty low number of days. 
```{r, out.width = '100%',fig.height=5}

boxplot<-comparison2 %>%
  filter(lakeName=="LittleRock")%>%
  ggplot(aes(x=dataset, y=mean, fill=dataset))+
  geom_boxplot(aes(ymin = GPP5,
                   lower = GPP25,
                   middle = GPP50,
                   upper = GPP75,
                   ymax = GPP95),
               stat='identity')+
  ggtitle("LittleRock Lake")+
  ylab(expression(paste('GPP (mg O2 m'^-2,' day'^-1,')')))+
  theme_bw()+
    scale_fill_manual(values=c("red","blue","green"))+
  theme(legend.position="none",
        axis.title.x=element_blank())

timeseries<-bella_metab_withMetaData %>%
  filter(lakeName=="LittleRock")%>%
  filter(GPP_mgm2<1)%>%
  ggplot(aes(x=solarDay,y=GPP_mgm2, fill=season))+
  geom_point(size=3, shape=21)+
  scale_fill_manual(values=c("lightgreen","white","forestgreen"))+
    ylab(expression(paste('GPP (mg O2 m'^-2,' day'^-1,')')))+
  theme_bw()

boxplot+timeseries +
  plot_layout(widths = c(1, 2))
```

<b>Trout Bog.</b> No discernable seasonal pattern here, but at least if we extend 'summer' out to Oct 1, we capture more of these relatively high GPP days.
```{r, out.width = '100%',fig.height=5}

boxplot<-comparison2 %>%
  filter(lakeName=="TroutBog")%>%
  ggplot(aes(x=dataset, y=mean, fill=dataset))+
  geom_boxplot(aes(ymin = GPP5,
                   lower = GPP25,
                   middle = GPP50,
                   upper = GPP75,
                   ymax = GPP95),
               stat='identity')+
  ggtitle("Trout Bog")+
  ylab(expression(paste('GPP (mg O2 m'^-2,' day'^-1,')')))+
  theme_bw()+
    scale_fill_manual(values=c("red","blue","green"))+
  theme(legend.position="none",
        axis.title.x=element_blank())

timeseries<-bella_metab_withMetaData %>%
  filter(lakeName=="TroutBog")%>%
  filter(GPP_mgm2<1 & GPP_mgm2>0.01)%>% 
  ggplot(aes(x=solarDay,y=GPP_mgm2, fill=season))+
  geom_point(size=3, shape=21)+
  scale_fill_manual(values=c("lightgreen","white","forestgreen"))+
    ylab(expression(paste('GPP (mg O2 m'^-2,' day'^-1,')')))+
  theme_bw()

boxplot+timeseries +
  plot_layout(widths = c(1, 2))
```

<b>Rotoiti</b>. Summer and summer+ estimates are identical because estimates for the shoulder season in this southern hemisphere lake are missing (Nov1-Dec and April1-May1). 
```{r, out.width = '100%',fig.height=5}

boxplot<-comparison1 %>%
  filter(lakeName=="Rotoiti")%>%
  ggplot(aes(x=dataset, y=mean, fill=dataset))+
  geom_boxplot(aes(ymin = GPP5,
                   lower = GPP25,
                   middle = GPP50,
                   upper = GPP75,
                   ymax = GPP95),
               stat='identity')+
  ggtitle("Lake Rotoiti")+
  ylab(expression(paste('GPP (mg O2 m'^-2,' day'^-1,')')))+
  theme_bw()+
    scale_fill_manual(values=c("red","blue","green"))+
  theme(legend.position="none",
        axis.title.x=element_blank())

timeseries<-bella_metab_withMetaData %>%
  filter(lakeName=="Rotoiti")%>%
  ggplot(aes(x=solarDay,y=GPP_mgm2, fill=season))+
  geom_point(size=3, shape=21)+
  scale_fill_manual(values=c("lightgreen","white","forestgreen"))+
    ylab(expression(paste('GPP (mg O2 m'^-2,' day'^-1,')')))+
  theme_bw()

boxplot+timeseries +
  plot_layout(widths = c(1, 2))
```



### When trimming results in >> GPP
Next I wanted to pull out a few lakes where trimming to 'summer' results in much higher estimates. 


<b>Kentucky.</b> Since we have an entire year of data in this lake, trimming by date (June1-Sept1) does a pretty good job of characterizing "peak" productivity, though we do miss the rising and falling limbs. If we add in the shoulder season ("+") we get a bit more days (still missing some relatively high GPP days), which brings down the mean/median. 
```{r, out.width = '100%',fig.height=5}

boxplot<-comparison2 %>%
  filter(lakeName=="Kentucky")%>%
  ggplot(aes(x=dataset, y=mean, fill=dataset))+
  geom_boxplot(aes(ymin = GPP5,
                   lower = GPP25,
                   middle = GPP50,
                   upper = GPP75,
                   ymax = GPP95),
               stat='identity')+
  ggtitle("Kentucky Lake")+
  ylab(expression(paste('GPP (mg O2 m'^-2,' day'^-1,')')))+
  theme_bw()+
    scale_fill_manual(values=c("red","blue","green"))+
  theme(legend.position="none",
        axis.title.x=element_blank())

timeseries<-bella_metab_withMetaData %>%
  filter(lakeName=="Kentucky")%>%
  ggplot(aes(x=solarDay,y=GPP_mgm2, fill=season))+
  geom_point(size=3, shape=21)+
  scale_fill_manual(values=c("lightgreen","white","forestgreen"))+
  scale_x_date(date_breaks = "5 weeks", date_labels = "%m-%d") +
  ylab(expression(paste('GPP (mg O2 m'^-2,' day'^-1,')')))+
  theme_bw()


boxplot+timeseries +
  plot_layout(widths = c(1, 2))
```



<b>Prairie Pothole</b> This is a NEON lake, where they used DO profilers rather than stationary DO sensors (among other continuity issues with their wind, temp sensors), so I ended up with a pretty low number of days. GPP is highly variable. Note that whether or not we trim the data, this lake is still one of the top 5 most productive in the dataset, FWIW. This range is still huge, though, and given the high number of missing values I'm inclined to throw away this lake.
```{r, out.width = '100%',fig.height=5}

boxplot<-comparison2 %>%
  filter(lakeName=="PrairiePothole")%>%
  ggplot(aes(x=dataset, y=mean, fill=dataset))+
  geom_boxplot(aes(ymin = GPP5,
                   lower = GPP25,
                   middle = GPP50,
                   upper = GPP75,
                   ymax = GPP95),
               stat='identity')+
  ggtitle("Prairie Pothole")+
  ylab(expression(paste('GPP (mg O2 m'^-2,' day'^-1,')')))+
  theme_bw()+
    scale_fill_manual(values=c("red","blue","green"))+
  theme(legend.position="none",
        axis.title.x=element_blank())

timeseries<-bella_metab_withMetaData %>%
  filter(lakeName=="PrairiePothole")%>%
  ggplot(aes(x=solarDay,y=GPP_mgm2, fill=season))+
  geom_point(size=3, shape=21)+
  scale_fill_manual(values=c("lightgreen","white","forestgreen"))+
    ylab(expression(paste('GPP (mg O2 m'^-2,' day'^-1,')')))+
  theme_bw()

boxplot+timeseries +
  plot_layout(widths = c(1, 2))
```

<b>Annie.</b> Similar case to Kentucky, where the estimates go up quite a bit because we are cutting out the least productive times of year. We do end up missing some relatively high GPP days with the Sept 1 cut-off, however. Adding in the shoulder seasons helps capture a few more relatively high GPP days, but overall brings down the mean a tiny bit.
```{r, out.width = '100%',fig.height=5}

boxplot<-comparison2 %>%
  filter(lakeName=="Annie")%>%
  ggplot(aes(x=dataset, y=mean, fill=dataset))+
  geom_boxplot(aes(ymin = GPP5,
                   lower = GPP25,
                   middle = GPP50,
                   upper = GPP75,
                   ymax = GPP95),
               stat='identity')+
  ggtitle("Lake Annie")+
  ylab(expression(paste('GPP (mg O2 m'^-2,' day'^-1,')')))+
  theme_bw()+
    scale_fill_manual(values=c("red","blue","green"))+
  theme(legend.position="none",
        axis.title.x=element_blank())

timeseries<-bella_metab_withMetaData %>%
  filter(lakeName=="Annie")%>%
  ggplot(aes(x=solarDay,y=GPP_mgm2, fill=season))+
  geom_point(size=3, shape=21)+
  scale_fill_manual(values=c("lightgreen","white","forestgreen"))+
  ylab(expression(paste('GPP (mg O2 m'^-2,' day'^-1,')')))+
  theme_bw()

boxplot+timeseries +
  plot_layout(widths = c(1, 2))
```


<b>Taihu</b>. Similarly, by excluding Oct-January we are capturing the most productive time of year in this lake. 
```{r, out.width = '100%',fig.height=5}

boxplot<-comparison2 %>%
  filter(lakeName=="Taihu")%>%
  ggplot(aes(x=dataset, y=mean, fill=dataset))+
  geom_boxplot(aes(ymin = GPP5,
                   lower = GPP25,
                   middle = GPP50,
                   upper = GPP75,
                   ymax = GPP95),
               stat='identity')+
  ggtitle("Lake Taihu")+
  ylab(expression(paste('GPP (mg O2 m'^-2,' day'^-1,')')))+
  theme_bw()+
    scale_fill_manual(values=c("red","blue","green"))+
  theme(legend.position="none",
        axis.title.x=element_blank())

timeseries<-bella_metab_withMetaData %>%
  filter(lakeName=="Taihu")%>%
  ggplot(aes(x=solarDay,y=GPP_mgm2, fill=season))+
  geom_point(size=3, shape=21)+
  scale_fill_manual(values=c("lightgreen","white","forestgreen"))+
    ylab(expression(paste('GPP (mg O2 m'^-2,' day'^-1,')')))+
  theme_bw()

boxplot+timeseries +
  plot_layout(widths = c(1, 2))
```

# Cutoff  for # of days missing
"Summer" is `r 244-152` days long and "summer+"/"extended summer" is `r 274-121` days long.
```{r, out.width = '100%',fig.height=5}
# glimpse(comparison1)
bella_metab_summer_summary %>%
  filter(dataset=="summer") %>%
  mutate(perc_missing_days=(n_NAs/91)*100)%>%
  ggplot(aes(x=reorder(lakeName, perc_missing_days), y=perc_missing_days))+
  geom_bar(stat="identity",  color="black", fill="blue")+
    theme(legend.position="none",
        axis.title.x=element_blank(),
        axis.text.x=element_text(angle = 45, hjust = 1, size=6))+
  geom_hline(yintercept=50)+
  ylab("Percentage of missing days during 'summer' period")

bella_metab_extendSummer_summary %>%
  # filter(dataset=="summer+") %>%
  mutate(perc_missing_days=(n_NAs/153)*100)%>%
  ggplot(aes(x=reorder(lakeName, perc_missing_days), y=perc_missing_days))+
  geom_bar(stat="identity",  color="black", fill="green")+
    theme(legend.position="none",
        axis.title.x=element_blank(),
        axis.text.x=element_text(angle = 45, hjust = 1, size=6))+
  geom_hline(yintercept=50)+
  ylab("Percentage of missing days during 'summer+' period")
```

Whether we consider just "summer" (June1-Sept1) or "summer+" (May1-Oct1), we end up with the same few lakes as problematic in terms of number of days missing. If we use 50% as a cut-off, these lakes are Balaton (borderline), Barco, PrairieLake, Prairie Pothole, and Rotoiti

# Cut-offs for lakes with lots of data
```{r, out.width = '100%',fig.height=15}

bella_metab_withMetaData %>%
  filter(lakeName %in% c("Simoncouche",
                         "Bay",
                         "Jordan",
                          "Castle",
                         "Mendota",
                         "P1",
                         "P8",
                         "Ovre",
                         "SkyPond",
                         "Vortsjarv",
                         "Sunapee",
                         "Crampton"))%>%
  ggplot(aes(x=solarDay,y=GPP_mgm2, fill=season))+
  geom_point(size=3, shape=21)+
  scale_fill_manual(values=c("lightgreen","white","forestgreen"))+
    ylab(expression(paste('GPP (mg O2 m'^-2,' day'^-1,')')))+
  theme_bw()+
    facet_wrap(.~lakeName, scales="free", ncol=3)


bella_metab_withMetaData %>%
  filter(lakeName %in% c("Taupo"))%>%
  ggplot(aes(x=solarDay,y=GPP_mgm2, fill=season))+
  geom_point(size=3, shape=21)+
  scale_fill_manual(values=c("lightgreen","white","forestgreen"))+
    ylab(expression(paste('GPP (mg O2 m'^-2,' day'^-1,')')))+
  theme_bw()+
    facet_wrap(.~lakeName, scales="free", ncol=3)

```


